---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VisualizacaoDados

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of VisualizacaoDados is to ...

## Installation

You can install the development version of VisualizacaoDados like so:

``` r
devtools::install_github("vitorcapdeville/VisualizacaoDados")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(VisualizacaoDados)
## basic example code
```


## Code of Conduct

Please note that the VisualizacaoDados project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

